---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

## Overview

`rstemlab` is a comprehensive R library designed for numerical analysis and computing in STEM fields. It provides tools for solving equations, performing simulations, analyzing data, and visualizing results, empowering researchers and students in science, technology, engineering, and mathematics.

## Installation

```{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("stemxresearch/rstemlab")
```

## Usage

To use the `rstemlab` package, you must start by loading it using the `library()` function as shown below.

```{r, message = FALSE}
library(rstemlab)
```

## Getting started

Click the **Get Started** link on the top menu or follow the link [Getting started](https://stemxresearch.github.io/rstemlab/articles/rstemlab.html) for a quick tutorial on the `rstemlab` library.

## Documentation

The **Reference** menu on the top menu or [this page](https://stemxresearch.github.io/rstemlab/reference/index.html) provides a list of all the functions available in the `rstemlab` package with help documentation including syntax and examples.

## Getting help

If you encounter a clear bug, please file an issue with a minimal reproducible example on [GitHub](https://github.com/stemxresearch/rstemlab/issues).

## Code of conduct

Please note that this project is released with a [Contributor Code of Conduct](https://www.r-project.org/coc-policy.html). By participating in this project you agree to abide by its terms.
